### 2021-12-11 thesis/tex/ICintro.tex
Lots of changes!!

\section{Neutrino detection}
\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}
% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

@@

\subsection{Atmospheric Neutrino Flux}
Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
These interactions ultimately produces pions, which decay as 
\begin{align}\label{eq:pion}
    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
\end{align}
The heavy muon ($m_\mu \approx 200m_e$) decays further:
\begin{align}
    &\mu^+ \to e^+ + \ne + \anm\,, \quad \mu^- \to e^- + \ane + \nm\,,
\end{align}
producing even more neutrinos.

>>>>

\section{Atmospheric Neutrino Flux}
Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
These interactions ultimately produces pions, which decay as 
\begin{align}\label{eq:pion}
    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
\end{align}
The heavy muon ($m_\mu \approx 200m_e$) decays further:
\begin{align}
    &\mu^+ \to e^+ + \ne + \anm\,, \quad \mu^- \to e^- + \ane + \nm\,,
\end{align}
producing even more neutrinos.

\section{Neutrino Detection}
\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}
% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

@@

### 2021-12-11 thesis/tex/ICtheory.tex
Lots of changes!!

Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$ by the collaboration. Thus, both $\mu$ and $\bar\mu$ will on average, experience the same $\Aeff$ in our model. 
Just as with the fluxes, we interpolate this in $\Etrue$ and $\ztrue$, and show the result in Fig.~\ref{fig:aeff}
Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area to which the array the leptons are exposed to.
While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than the flux itself. Energy-wise, the situation here is completely reverse from the flux. Increasing with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.

@@

@@

We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
correction factors of Eq.~\ref{eq:MC_norm}.
\begin{figure}[ht]
    \begin{centering}
    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
    \end{centering}
\end{figure} 
Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.
% \newpage
% \bibliographystyle{nature}
% \bibliography{ref.bib}
% \end{document}

>>>>

Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$ by the collaboration. Thus, both $\mu$ and $\bar\mu$ will on average, experience the same $\Aeff$ in our model. 
Just as with the fluxes, we interpolate this in $\Etrue$ and $\ztrue$, and show the result in Fig.~\ref{fig:aeff}
Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area to which the array the leptons are exposed to.
While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than the flux itself. Energy-wise, the situation here is completely reverse from the flux. 
Increasing linearily with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.

@@

Note that since atmospheric neutrino flux scales as $E^{-2.7}$, the log-normal Gaussian $R(E^r, E^t)$ as $E^{-2}$,
and the effective area is approximately linear in $E$.
Thus, the event count in~\ref{eq:ICevents} will be proportional to $E^{-1.7}$. Having almost a quadratic dropoff, the event count as 
observed by IceCube will be lower and lower as we probe higher energies, severely limiting our confidence in \si{\TeV} analyses due to 
lower statistical significance.

@@

We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
correction factors of Eq.~\ref{eq:MC_norm}.
\begin{figure}[ht]
    \begin{centering}
    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
    \end{centering}
\end{figure} 
Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.

### 2021-12-11 thesis/tex/nsiResults.tex
Lots of changes!!

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.38\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
\end{figure}
%TODO 5.6 is small, fix labels
%TODO:  Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation. 
The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.

\begin{figure}
   \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
   \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out.}\label{fig:PINGU_2D}
\end{figure}

>>>>

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.47\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.51\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
\end{figure}
%TODO 5.6 is small, fix labels
There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation. 
The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$.

\begin{figure}
   \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
   \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out. The values of the standard oscillation parameters 
   are taken from NuFit~\cite{nufit}.}\label{fig:PINGU_2D}
\end{figure}

### 2021-12-11 thesis/tex/nsiTheory.tex
Lots of changes!!

% \documentclass{thesis}
% \usepackage[margin=0.5in]{geometry}
% \input{commands}
% \usepackage{siunitx, graphicx}
% \usepackage[utf8]{inputenc}
% \usepackage{xr-hyper}

% \begin{document}
\section{Non-Standard Interactions}\label{sec:nsiTheory}
We have no reason to believe that the Standard Model 
gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
oscillations force us to amend it. 
Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with completely different
properties might undergo a similar spontaneous symmetry break at high energies, 
producing at lower energies the Standard Model that we know. In fact, 
just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
another broken symmetry resulting in the Standard Model gauge group.
In this sense, the Standard Model might be considered 
an effective low energy theory, which is yields impressive results in some areas, but failing in others.

@@

\subsection{IceCube Signal}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
the IceCube data is available in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have settled down.

@@

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
        \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilites simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

@@

\subsection{DeepCore and PINGU Signals}
Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have settled down.

>>>>

\section{Non-Standard Interactions}\label{sec:nsiTheory}
We have no reason to believe that the Standard Model 
gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
oscillations force us to amend it. 
Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with completely different
properties might undergo a similar spontaneous symmetry break at high energies, 
producing at lower energies the Standard Model that we know. In fact, 
just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
another broken symmetry resulting in the Standard Model gauge group.
In this sense, the Standard Model might be considered 
an effective low energy theory, which is yields impressive results in some areas, but failing in others.

@@

\subsection{IceCube Signal}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
the IceCube data is available in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have averaged out.

@@

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
        \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilites simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

@@

\subsection{DeepCore and PINGU Signals}
Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have averaged out.

### 2021-12-11 thesis/tex/oscillations.tex
Lots of changes!!

By construction, it provides the unitary transformation between the flavor and mass bases.
Any unitary $3\times3$ matrix can be parametrized using three angles and six phases. However, not all phases affect the 
charged and weak currents and are thus not observable by us. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
leaving only one physical phase for us to measure: one term in the form of a Dirac CP-violating phase $\delta_\mathrm{CP}$.
However, if the neutrinos are Majorana fermions, the rephasing of the left-handed fields would cause the neutrino masses to become complex.
Thus, we include two Majorana phases $\lambda_{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number.

We are now down to six degrees of freedom in the three dimensional case: three angles
of the form $s_{ij}, c_{ij}$, and three phase of the form $e^{i\delta_\mathrm{CP}}$ and $e^{i\lambda_{i}}$. The angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate. The physical interpretation of
a mixing angle is then the degree to which the $\nu_i$ mass eigenstate mixes with the $\nu_j$ mass eigenstate. Thus we refer to $\theta_{ij}$ as the mixing angles. A non-zero mixing angle will then 
cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates $\nu_i$ that we allowed to mix. More on this in Section~\ref{sec:prop}.

@@

\begin{align}\label{eq:eff_theta}
    \tan{(2\theta_{12}^M)} = \frac{\tan{(2\theta_{12})}}{1- \frac{2\sqrt{2}G_F N_e E}{\dm[21]\cos{(2\theta_{12})}}}\,.
\end{align}
Eq.~\ref{eq:eff_theta} has a pole at %TODO: write more
\begin{align}
    E^* &= \frac{\dm[21]\cos(2\theta_{12})}{2\sqrt{2}G_F N_e}\,.
\end{align}
So at a certain electron density, a neutrino with energy $E^*$ will experience a resonance in the matter mixing angle. This phenomenon is called MSW resonance after Mikheev, Smirnov, and Wolfenstein. At this point, $\tan{(2\theta_{12}^M)} \to \infty$, which is equivalent to the matter mixing angle $\theta_{12}^M$ assuming its maximal value, $\pi/4$. Thus, the MSW resonance can cause maximal mixing between two flavors.

@@

\subsection{Earth propagation}
We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
symmetric piecewise polynomials for the Earth density in \si{\gram\cm^-3} shown in the left panel of Fig.~\ref{fig:potential}.
We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
oscillations.

@@

\begin{figure}
    %TODO: labels, caption. Include osc params used. Mention value of L if missing.
    % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
    \centering
    \includegraphics[width=0.7\textwidth]{figures/oscillations.pdf}
    \caption{}\label{fig:oscillations}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/oscillograms.pdf}
    \caption{Oscillograms showing neutrino oscillations for all flavors in $E - \cos(\theta_z)$ space. Note the panels are symmetric about the diagonal panels, i.e. $P_{\a\b} = P_{\b\a}$ due to $\delta_{CP} = 0$. The core-mantle boundary from Fig.~\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.}\label{fig:oscillograms}%TODO: redo finer
\end{figure}%TODO: remake with finer

% \end{document}

>>>>

By construction, it provides the unitary transformation between the flavor and mass bases.
Any unitary $3\times3$ matrix can be parametrized using three angles and six phases. However, not all phases affect the 
charged and weak currents and are thus not observable by us. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
leaving only one physical phase for us to measure: one term in the form of a Dirac CP-violating phase $\delta_\mathrm{CP}$.
However, if the neutrinos are Majorana fermions, the rephasing of the left-handed fields would cause the neutrino masses to become complex.
Thus, we include two Majorana phases $\lambda_{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number, and a Majorana phase would
violate lepton number by two units.

We are now down to six degrees of freedom in the three dimensional case: three angles
of the form $s_{ij}, c_{ij}$, and three phase of the form $e^{i\delta_\mathrm{CP}}$ and $e^{i\lambda_{i}}$. The angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane. The physical interpretation of
a mixing matrix element $U_{ij}$ is then the degree to which the $\nu_i$ mass eigenstate mixes with the $\nu_j$ mass eigenstate. Thus we refer to $\theta_{ij}$ as the mixing angles. A non-zero mixing angle will then 
cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates $\nu_i$ that we allowed to mix. More on this in Section~\ref{sec:prop}.

@@

\begin{align}\label{eq:eff_theta}
    \tan{(2\theta_{12}^M)} = \frac{\tan{(2\theta_{12})}}{1- \frac{2\sqrt{2}G_F N_e E}{\dm[21]\cos{(2\theta_{12})}}}\,.
\end{align}
Eq.~\ref{eq:eff_theta} has a pole at %TODO: write more
\begin{align}\label{eq:MSW}
    E^* &= \frac{\dm[21]\cos(2\theta_{12})}{2\sqrt{2}G_F N_e}\,.
\end{align}
So at a certain electron density, a neutrino with energy $E^*$ will experience a resonance in the matter mixing angle. This phenomenon is called MSW resonance after Mikheev, Smirnov, and Wolfenstein. At this point, $\tan{(2\theta_{12}^M)} \to \infty$, which is equivalent to the matter mixing angle $\theta_{12}^M$ assuming its maximal value, $\pi/4$. Thus, the MSW resonance can cause maximal mixing between two flavors.

@@

\subsection{Earth propagation}
We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
symmetric piecewise polynomials for the Earth density in \si{\gram\cm^{-3}} shown in the left panel of Fig.~\ref{fig:potential}.
We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
oscillations.

@@

\begin{figure}
    %TODO: labels
    % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
    \centering
    \includegraphics[width=0.7\textwidth]{figures/oscillations.pdf}
    \caption{Neutrino oscillation probabilities after traversing the diameter of the Earth. 
    Oscillation parameters are taken from NuFit~\cite{nufit} and given in Eq.~\ref{eq:PINGUparams}.}\label{fig:oscillations}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/oscillograms.pdf}
    \caption{Oscillograms showing neutrino oscillations for all flavors in $E - \cos(\theta_z)$ space. Note the panels are symmetric about the diagonal panels, i.e. $P_{\a\b} = P_{\b\a}$ due to $\delta_{CP} = 0$. The core-mantle boundary from Fig.~\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.}\label{fig:oscillograms}%TODO: redo finer
\end{figure}
